---
title: "Lab 02 - Take a sad plot and make it better"
author: "Group Members: Fuhong, Alex, Wuhaotian and Kevin GU"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
staff <- read_csv("data/instructional-staff.csv")
```


--------


Team member 1 should pull to download updates and begins here.



### Exercise 1

There would be 55 rows.


Team member 1 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 2 should pull to download updates and begins here.

### Exercise 2

```{r staff-long-create}
# uncomment and edit the code below
staff_long <- staff %>%
  pivot_longer(
    cols = -faculty_type, 
    names_to = "Year",
    values_to = "percentage_of_faculty"
      )
```


### Exercise 3

We got the same amount of rows as Q1 (55)

```{r staff-long-inspect}
nrow(staff_long)
```


Team member 2 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 3 should pull to download updates and begins here.


### Exercise 4

there is no line on the plot and years are too close to each other.

```{r lineplot-1}
staff_long %>% 
  ggplot(aes(x = Year, 
             y =  percentage_of_faculty, colour = faculty_type)) +
  geom_line()
```


### Exercise 5

*Remove this text and add your answer here.*

```{r lineplot-2}
staff_long %>% 
 
  ggplot(mapping = aes(x = Year, 
             y =  percentage_of_faculty, colour = faculty_type, group = faculty_type)) +
  geom_line()
```


Team member 3 should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 6

*Remove this text and add your answer here.*

```{r lineplot-3}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 7

*Remove this text and add your answer here. No code needed for this exercise!*


### Exercise 8

*Remove this text and add your answer here.*

```{r lineplot-4}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

All team members should pull to download all updates.


